---
title: "Workflow for Ridgway's Hawk NON-Integrated Population Model"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index-simp.html'))})
author: "Brian W. Rolek"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/modelcheck-simp.R')
```

# Model estimates
```{r,setup, eval=TRUE, warning=FALSE, message=FALSE}
```

Plot model estimates of demographic rates. Life Stages are abbreviated as B = breeder, NB = nonbreeder, FY = first year. First-year abundance accounts for translocated birds. 
# Print parameter estimates
Parameter estimates for input into a population viability analysis.

```{r,catplots, eval=TRUE, warning=FALSE, message=FALSE}
```

# Fecundity
```{r,fecundity, eval=TRUE, warning=FALSE, message=FALSE}
```

# Print parameter estimates
Parameter estimates for input into a population viability analysis.

```{r,tables, eval=TRUE, warning=FALSE, message=FALSE}
```

# Model diagnostics
```{r,traceplots, eval=TRUE, warning=FALSE, message=FALSE}
```

```{r,fit, eval=TRUE, warning=FALSE, message=FALSE}
```