---
title: "Workflow for Ridgway's Hawk Integrated Population Model"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Brian W. Rolek"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Supplemental materials for: 
Brian W. Rolek, Leah Dunn, Marta Curti, Russell Thorstrom, Evan Buechley, Carolina Granthon, Jeff Johnson, Carlos Suárez, Gabriela Diaz, and Christopher J. W. McClure. 2025. Management influences population persistence of the Critically Endangered Ridgway’s Hawk (Buteo ridgwayi) and creates tradeoffs between sites

Contact information: rolek.brian@peregrinefund.org

A permanent archive and DOI is available at: 
<https://zenodo.org/doi/XXXXX>

Metadata, data, and scripts used in analyses can be found at <https://github.com/The-Peregrine-Fund/Ridgways-Hawk-IPM>.

The full workflow below is visible as a html website at:
<https://the-peregrine-fund.github.io/Ridgways-Hawk-IPM/>.

-----------------------------------------------------------------------   
# 1. Integrated Population Model (IPM)

## 1.1 Model Code 
Code for the Integrated Population Model. 
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/03-ipm.R')
```
```{r,ipm, eval=FALSE, warning=FALSE, message=FALSE}
```

## 1.2 Results- Figures and Tables
Simple summary statistics 
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/05-postprocess.R')
```
```{r,postprocess, eval=TRUE, warning=FALSE, message=FALSE}
```

### 1.2.1 Population Trends and Structure 
```{r,trends, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 4)}
```

```{r,popstructure, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(6, 8)}
```

### 1.2.2 Apparent Survival, Recruitment, and Detection 
```{r,survival, eval=TRUE, warning=FALSE, message=FALSE}
```

### 1.2.3 Productivity
```{r,productivity, eval=TRUE, warning=FALSE, message=FALSE}
```

### 1.2.4 Correlations Among Parameters
R is the correlation coefficent between rates. Indices for R are demographics and detection parameters in both dimensions. For example, R[1,2] is the correlation coefficient between first-year survival and nonbreeder survival.   
1. First-year Survival  
2. Nonbreeder Survival   
3. Breeder Survival   
4. First-year recruitment to breeder  
5. Nonbreeder recruitment to breeder  
6. Breeder transition to nonbreeder  
7. Nonbreeder detection  
8. Breeder detection  
9. Productivity  

```{r,cors_demo, eval=TRUE, warning=FALSE, message=FALSE}
```

### 1.2.5 Population Growth Rates Over Time
```{r,popgr, eval=TRUE, warning=FALSE, message=FALSE}
```

### 1.2.6 Correlations Between Population Growth Rates and Demographics
```{r,cors1, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 12)}
```

### 1.2.7 Transient Life Table Response Experiments (tLTREs)  
Population Growth Rates and Contributions from Demographics
```{r,contributions, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(8, 6)}
```

# 2. Population Viability Analysis (PVA)

## 2.1 Model Code
Code for Population Viability Analysis.
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/04-pva.R')
```
```{r,pva, eval=FALSE, warning=FALSE, message=FALSE}
```

## 2.2 PVA Projections
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/05-postprocess.R')
```

### 2.2.1 Local Extinction Probability 
```{r,pva_ext1, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 12)}
```

```{r,pva_ext2, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 8)}
```

### 2.2.3 Abundance 
```{r,pva_abund, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 12)}
```

### 2.2.4 Percent Change in Abundance
```{r,pva_pc, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 8)}
```

### 2.2.5 Probability of Decline in Abundance
```{r,pva_pd, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 8)}
```

### 2.2.6 Time to Extinction
```{r,pva_tt_ext, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 12)}
```

# 3. Additional IPM plots

## 3.1 Model Diagnostics
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/modelcheck.R')
```

```{r,setup, eval=TRUE, warning=FALSE, message=FALSE}
```

```{r,pltfunction, eval=TRUE, warning=FALSE, message=FALSE}
```

### 3.1.1 Check Goodness-of-fit
Goodness-of-fit tests provide evidence that statistical distributions adequately describe the data. Here we test fit for brood size and counts. A Bayesian p-value nearest to 0.5 suggests good fitting statistical distributions, while values near 1 or 0 suggest poor fit.

```{r,fit, eval=TRUE, warning=FALSE, message=FALSE}
```

### 3.1.2 Examine Traceplots, Compare Posteriors with Priors
Traceplots provide evidence that models adequately converged.

```{r,traceplots, eval=TRUE, warning=FALSE, message=FALSE}
```

## 3.2 Demographics- Annual Averages
```{r,demo_avs, eval=TRUE, warning=FALSE, message=FALSE}
```


## 3.3 Abundance of Finer Population Segments

Plot model estimates of demographic rates. Life Stages are abbreviated as B = breeder, NB = nonbreeder, FY = first year. First-year abundance accounts for translocated birds. 

Population dynamics are determined by transitions, These transitions between stages are abbreviated as the starting life stage to the final life stage. For example a first-year recruiting to a breeder would be abbreviated as "FY to B". I'll list them here for convenience:  
* "FY to NB" is first-year to nonbreeder.  
* "NB to NB" is nonbreeder adult to nonbreeder adult.  
* "B to NB" is a breeding adult to a nonbreeder adult.  
* "FY to B" is first-year to breeder.  
* "NB to B" is nonbreeder adult to breeder adult.  
* "B to B" is breeder adult to breeder adult.  

```{r,catplots2, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 14)}
```
