---
title: "Workflow for Ridgway's Hawk Integrated Population Model"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Brian W. Rolek"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Supplemental materials for: Rolek, B.W., McClure, CJW, Dunn, L., Curti, M., ... Ridgway's Hawk IPM and PVA

Contact information: rolek.brian@peregrinefund.org

Metadata, data, and scripts used in analyses can be found at <https://github.com/The-Peregrine-Fund/XXXXX>.

The full workflow below is visible as a html website at:
<https://the-peregrine-fund.github.io/XXXXX/>.

A permanent archive and DOI is available at: https://zenodo.org/doi/XXXXX

----------------------------------------------------------------------- 
# Plot model estimates
```{r, include=FALSE, cache=FALSE, warning=FALSE }
knitr::read_chunk('R/modelcheck.R')
```
```{r,setup, eval=TRUE, warning=FALSE, message=FALSE}
```

```{r,pltfunction, eval=TRUE, warning=FALSE, message=FALSE}
```


Plot model estimates of demographic rates. Life Stages are abbreviated as B = breeder, NB = nonbreeder, FY = first year. First-year abundance accounts for translocated birds. 

```{r,catplots1, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 14)}
```

Population dynamics are determined by transitions, These transitions between stages are abbreviated as the starting life stage to the final life stage. For example a first-year recruiting to a breeder would be abbreviated as "FY to B". I'll list them here for convenience:

"FY to NB" is first-year to nonbreeder.

"NB to NB" is nonbreeder adult to nonbreeder adult.

"B to NB" is a breeding adult to a nonbreeder adult.

"FY to B" is first-year to breeder.

"NB to B" is nonbreeder adult to breeder adult.

"B to B" is breeder adult to breeder adult.

```{r,catplots2, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 14)}
```

Other parameter estimates. 
```{r,catplots3, eval=TRUE, warning=FALSE, message=FALSE}
```

# Stage Structure of Each Population
```{r,popstructure, eval=TRUE, warning=FALSE, message=FALSE}
```

# Correlations between population growth rates and demographics
```{r,popgrowth, eval=TRUE, warning=FALSE, message=FALSE, fig.dim = c(10, 5)}
```  

# Print parameter estimates
Parameter estimates for input into a population viability analysis.

```{r,paramests, eval=TRUE, warning=FALSE, message=FALSE}
```

# Model diagnostics

## Check Goodness-of-fit
Goodness-of-fit tests provide evidence that statistical distributions adequately describe the data. Here we test fit for brood size and counts. A Bayesian p-value nearest to 0.5 suggests good fitting statistical distributions, while values near 1 or 0 suggest poor fit.

```{r,fit, eval=TRUE, warning=FALSE, message=FALSE}
```

## Examine Traceplots, omitted to reduce file size
<!-- Traceplots provide evidence that models adequately converged. -->

<!-- ```{r,traceplots, eval=TRUE, warning=FALSE, message=FALSE} -->
<!-- ``` -->

